Convolutional Neural Networks and Volcano Plots: Screening and Prediction of Two-Dimensional Single-Atom Catalysts for CO\textsubscript{2} Reduction Reactions

### 2024-02-16 paper/writing-version/supp_3_ml.tex
rename dir
use eDOS over DOS globally

The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{supp_fig20:input_dos}.
Here, ``numSamplings'' represents the number of data points sampled across the energy spectrum,
``numOrbitals'' denotes the number of DOS orbitals,
and ``numChannels'' indicates the number of atomic channels.

@@

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
\label{supp_table18:cnn_mae}
  \caption{Prediction mean absolute errors of the CNN model.}
  \small
  \begin{tabularx}{\textwidth}{@{}lXX@{}}
    \toprule
    Adsorbate             & Original dataset (eV)  & Augmented dataset (eV)  \\
    \midrule
    CO\textsubscript{2}   & 0.0447                 & 0.0336                  \\
    COOH                  & 0.0436                 & 0.0581                  \\
    CO                    & 0.0402                 & 0.0402                  \\
    CHO                   & 0.0614                 & 0.0778                  \\
    CH\textsubscript{2}O  & 0.0553                 & 0.0632                  \\
    OCH\textsubscript{3}  & 0.0605                 & 0.0636                  \\
    O                     & 0.1135                 & 0.1081                  \\
    OH                    & 0.0547                 & 0.0602                  \\
    H                     & 0.0703                 & 0.0646                  \\
    \bottomrule
  \end{tabularx}

@@

  \footnotesize\textit{Note:} The same CNN model, trained on the
    augmented dataset, was used for all predictions. The term ``original dataset''
    refers to evaluations conducted on the original dataset without any augmented data;
    it does not imply the use of a different CNN model trained solely on the original dataset.
    Similarly, ``augmented dataset'' refers to evaluations on the dataset with
    both original data and augment data, not a distinct model.
\end{table}

>>>>

The format of the 2D array for the eDOS is naturally well-suited for use as neural network inputs.
In this study, the array adopts a shape of [numSamplings, numOrbitals, numChannels], as illustrated in \cref{supp_fig20:input_dos}.
Here, ``numSamplings'' represents the number of data points sampled across the energy spectrum,
``numOrbitals'' denotes the number of eDOS orbitals,
and ``numChannels'' indicates the number of atomic channels.

@@

% Supplementary Table 18: Prediction MAEs of the CNN model
\begin{table}[htbp]
\label{supp_table18:cnn_mae}
  \caption{Prediction mean absolute errors of the CNN model.}
  \small
  \center
  \begin{tabularx}{0.75\textwidth}{@{}lXX@{}}
    \toprule
    Adsorbate             & Original dataset (eV)  & Augmented dataset (eV)  \\
    \midrule
    CO\textsubscript{2}   & 0.0447                 & 0.0336                  \\
    COOH                  & 0.0436                 & 0.0581                  \\
    CO                    & 0.0402                 & 0.0402                  \\
    CHO                   & 0.0614                 & 0.0778                  \\
    CH\textsubscript{2}O  & 0.0553                 & 0.0632                  \\
    OCH\textsubscript{3}  & 0.0605                 & 0.0636                  \\
    O                     & 0.1135                 & 0.1081                  \\
    OH                    & 0.0547                 & 0.0602                  \\
    H                     & 0.0703                 & 0.0646                  \\
    \bottomrule
  \end{tabularx}

@@

  \begin{flushright}
  \begin{minipage}{\textwidth}
    \footnotesize\textit{Note:} The same CNN model, trained on the
      augmented dataset, was used for all predictions. The term ``original dataset''
      refers to evaluations conducted on the original dataset without any augmented data;
      it does not imply the use of a different CNN model trained solely on the original dataset.
      Similarly, ``augmented dataset'' refers to evaluations on the dataset with
      both original data and augment data, not a distinct model.
  \end{minipage}
  \end{flushright}
\end{table}
